---
title: "Readme"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DiagrammeR)
```

## Scope

This is a very small sample shiny app to illustrate how to work with files in
the server operating system in a reactive mode.

Even when run on one's own local computer, a Shiny app contains both a client
part and a server part that communicate through the TCP/IP network. Thus,
the included `fileInput` function supplied with shiny works by "uploading" files
through the network from the browser environment, and `downloadHandler` saves files
by transferring them through the network to the users Downloads directory
(typically), even though the both parts of Shiny ar running on the same computer.

It can be simpler and more efficient to simply load files into the Shiny R server
using normal file read and write functions, but having a user dialog to give
control over which files are read or written to is still needed. Enter the
`shinyFiles` package.

## Reactive flow

```{r digraph, error=FALSE}
grViz(
'digraph shinyFileProc {
node [shape=rect]
file1 [label="input$file1"]
testfile_csv [label="testfile.csv"]
testfile_muck_csv [label="testfile_muck.csv"]
node [style=rounded]
fnamer
dtar
fname_muckr
outputfile1summary [label="output$file1summary"]
node [shape=oval]
file1 -> parseFilePaths
parseFilePaths -> finfo
finfo -> fnamer
testfile_csv -> read_csv [style=dotted]
read_csv [label="read.csv"]
fnamer -> read_csv
read_csv -> dtar
fnamer -> fname_muckr
dtar -> muck
muck -> write_muck
fname_muckr -> write_muck
write_muck -> testfile_muck_csv [style=dotted]
write_muck -> outputfile1summary
}
')
```

- `input$file1`: character, path to selected input file
- `parseFilePaths`: function, works in conjunction with `shinyFileChoose` to
  provide a data frame of one or more rows describing the file name and directory.
- `finfo`: data frame, containing name of file and full path to file (`datapath`).
- `fnamer`: reactive path to input filename. As this is updated, any reactives
that depend upon it and get directly or indirectly triggered by a need to
display output will get updated.
- `read.csv`: function, any R input function can be used as needed... this is
just to show how it is used.
- `dtar`: reactive data frame containing contents of input file.
- `muck`: function to serve as an example of doing "something" to a data frame.
- `fname_muckr`: sample way to create an output filename based on the input
filename.
- `write_muck`: function to write out the modified data frame to a new output
file. Returns something to display on the screen to indicate whether it succeeded...
in this case, the number of rows that were processed. The item to display on
the screen is not important of itself, but the fact that it needs to be displayed
is what causes Shiny to start working through the dependency graph of the reactive
objects, causing the the whole chain of dependencies to be executed.

